Sequential rank agreement methods for comparison of ranked lists

### 2015-04-07 latex/paper.Rnw
Diverse
asd

\documentclass[12pt,a4paper]{article}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\usepackage{subcaption}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

@@

@@

We now describe what is exemplified in Panel (c) of Table
\ref{tab:example} and how it can be used to define \emph{sequential
  rank agreement}. For an integer $1\le d\le P$ we define the unique
set of items found in the $L$ top $d$ parts of the lists, i.e., the
set of items ranked less than or equal to $d$ in any of the lists:
\begin{equation}
S_d = \{\pi_l(r) ; r \leq d, l = 1, \ldots, L \}.
\end{equation}
The \emph{sequential rank agreement} is the pooled standard deviation
of the items found in the set $S_d$:
\begin{equation}
\textrm{SRA}(d)= \sqrt{\frac{\sum_{\{p \in S_d\}}(L-1)A(p)^2}{(L-1)|S_d|}}.
\end{equation}

\subsection{All lists fully observed}
We shall start by the simplest case where all $L$ lists are fully observed.

@@

@@

@@

@@

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage[]{color}
\usepackage{subcaption}
\usepackage{natbib}
\usepackage{xspace}
\usepackage[noae]{Sweave}

%
% New commands
%
\newcommand{\ie}{\emph{i.e.,}\@\xspace}
\newcommand{\eg}{\emph{e.g,}\@\xspace}

@@

Key words: sequential rank agreement, rank agreement, order statistic,
methods comparison, variable selection

@@

We now describe what is exemplified in Panel (c) of Table
\ref{tab:example} and how it can be used to define \emph{sequential
  rank agreement}. For an integer $1\le d\le P$ we define the unique
set of items found in the $L$ top $d$ parts of the lists, i.e., the
set of items ranked less than or equal to $d$ in any of the lists:
\begin{equation}
S_d = \{\pi_l(r) ; r \leq d, l = 1, \ldots, L \}.
\end{equation}
The \emph{sequential rank agreement} is the pooled standard deviation
of the items found in the set $S_d$:
\begin{equation}
\textrm{SRA}(d)= \sqrt{\frac{\sum_{\{p \in
      S_d\}}(L-1)A(p)^2}{(L-1)|S_d|}}, \label{def:sra}
\end{equation}
and small values close to zero suggests that the lists agree on the
ordering while larger values suggests disagreement. If the ranked
lists are identical then the value of SRA will be zero for all depths
$d$.  The sequential rank agreement can be interpreted as the average
distance of the individual rankings of the lists from the average
ranking for each of the items we have seen until depth $d$.

\subsection{All lists fully observed}
We shall start by the simplest case where all $L$ lists are fully
observed, \ie, we have the rank of all $P$ items for all of the $L$
lists. This situation occurs is common when we have the original
dataset available and when we wish to, say, compare the results from
different analysis methods.

For the fully obseved list situation we can plot the sequantial
rank agreement \eqref{def:sra} as a function of depth $d$. If there is
a ... An example is seen in Figure~\ref{XX}

@@

Noget med

@@

Three approaches

\subsection{Independent lists}

\subsection{Permuted outcomes + analyses}

Do the following a large number of times
\begin{enumerate}
  \item Permute outcome vector
  \item Redo analyses for all $L$ methods
  \item Compute sequential rank agreement for 
\end{enumerate}

Lidt spøjs ting man matcher dem op imod

\subsection{Changepoint analysis}

@@

In a classical paper by \citet{Golub1999} a dataset of 3051 gene
expression values were measured on 38 tumor mRNA samples in order to
improve the classification of acute leukemias between two types: acute
lymphoblastic leukemia (ALL) or acute myeloid leukemia
(AML). Preprocessing of the gene expression data was done as described
in \citep{Dudoit2002}.

We analyzed these gene expression data using five different
approaches:

@@

\bibliographystyle{apalike}
\bibliography{paperref}
